\textbf{Discovery of a disrupting open cluster in the Galactic halo:\\ a recent star formation event in the leading arm of the Magellanic stream}

### 2018-11-03 ms.tex
methods description

In the subsections below, we perform two independent analyses of the data available for \clustername.
In \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to identify members probabilistically, then demonstrate that the high-probability kinematic members appear as a clear young main sequence in the \gaia\ CMD.
In \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to again identify members probabilistically, and simultaneously infer the cluster parameters (age, metallicity, distance, etc.).
We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.

>>>>

In the subsections below, we perform two independent analyses of the data available for \clustername.
First, in \sectionname~\ref{sec:pmclean}, we use astrometric data from \gaia\ \DR{2} to determine the mean proper motion of the cluster by modeling the kinematics of the cluster and background sources.
Then, in \sectionname~\ref{sec:popmodel}, we use photometric data from \decam\ to assign membership probabilities to sources and simultaneously infer the cluster stellar population parameters (age, metallicity, distance, etc.).
We perform these analyses separately because \gaia\ \DR{2} only includes the most massive members of the cluster, but the addition of lower main sequence members apparent in the \decam\ photometry provide a much better constraint on the cluster parameters.
